### 2016-06-07 R/ITHIM.Rmd
Added code to loop through values of muwt

>>>>

```{r parlist}
AF.sum <- numeric(1e3); i <- 0;
muwt.vec <- seq(107.1,150,length.out=length(AF.pseudo))
#muct.vec <- seq(2.7,3.0,length.out=length(AF.pseudo))
for(muwt in muwt.vec){
i <- i+1
parameters <- createParameterList(baseline = FALSE)

parameters <- setParameter(parName="muwt", parValue = muwt, parList = parameters)
ITHIM.scenario <- list(
  parameters = parameters <- parameters,
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
comparitiveRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
AF.sum[i] <- with(comparitiveRisk, sum(100*AF$BreastCancer))
}
D <- data.frame(mu.wt = muwt.vec,AF.sum=AF.sum)
p <- ggplot(D, aes(x = mu.wt, y = AF.sum))
p + geom_point()
```
